---
title: "Rose diagram for fault analysis"
subtitle: "An implementation in R Markdown - Tufte Handout"
author: "Marc Boulet"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, message=FALSE, error=FALSE, warning=FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```
# Summary

This document is designed to display a rose diagram. The data is taken from Sarah Grant's fault mapping.^[Faults 12 and 13 are dummy values used to ensure that the plot displays 0-360 degrees.]

```{r data_load}
library(readr)
library(knitr)
sarah_faults <- read_csv("~/rosediagram/data/sarah_faults.csv")
kable(sarah_faults)  
```  
  
    
    
# Rose diagram using ggplot
This diagram uses ggplot.^[Nice presentation with thin area bars and full colour control, though it is missing interactivity.]

```{r rose_diagram_ggplot, echo=TRUE, fig.height=8, fig.width=8, warning=FALSE}
library(ggplot2)
ggplot(sarah_faults, aes(x = azimuth, y = magnitude, fill= magnitude)) +
        coord_polar(theta = "x", start = -.04) +
        geom_col(width = 5, alpha = 0.5) +
        scale_x_continuous(breaks = seq(0, 360, 30))
```

# Rose diagram using plotly
This diagram uses plotly.^[Nice presentation with great interactivity and axis ticks inside the plot. Bars are too wide, however.]
```{r rose_diagram_plot.ly, warning=FALSE}
library(plotly)
p <- plot_ly(sarah_faults, r = ~magnitude, t = ~azimuth, type = "area", 
             colors = "green", alpha=0.3)
layout(p, radialaxis = list(), orientation = -90)
```

